% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{lipsum}

\usepackage{comment} %OSCARs insert

\section{Appendix 1}

\subsection{Statement of team roles/contributions}

All team members conducted auto-ethnography, online semi-structured interviews, and photography ethnography, as well in transcribing and analyzing the collected data in Temi and Miro. We all remained in constant contact throughout the project, and each contributed valuable and creative input. The conference paper is written by the team together. However, the headlines have had main authors and secondary authors. Below you will find a brief overview of the individuals' roles and areas of responsibility. 

\subsection{Andreea Roman}

Contributed with the preparation of the Industry Presentation, the creation of the leaflet included in it (with the illustrations from the designer). Worked on Findings of Auto-ethnography, Photo ethnography, Conclusion and Future work. Helped with Miro organization.  

\subsection{Dragos-Alexandru Gabor} 

Contributed by creating the consent forms and information sheets. Coordinated the e-signing effort between researchers and participants. Helped organize the Miro board before meetings. Set up the LaTeX report. Within the final report, worked mainly on Abstract, Introduction, Related work, Auto-ethnography, Implications for design. 

\subsection{Joanna Zamiechowska}

Worked mainly on the Interview Methodologies and Findings section, partly in Discussions, Implications for Design, and Conclusions and Future Work, with secondary contributions in other sections throughout the paper. Researched semi-structured interview methodology. Researched literature and contributed literature in the references. Chief editor and proofreader, with contribution from the other teammates in this effort. 

\subsection{Oscar Larsson}

Team coordinator, logistics coordinator, and contact person for the university. Responsible for submitting work assignments in TUWEL. Set up the “MS Teams platform” which has been our main information arena in the research project. Here we have structured and analyzed our data, as well as reviewed our internal documents and deadlines. Main author of the headings Introduction, RQ, Discussion, and Conclusion and Future Work. Secondary author of the headlines Abstract and Related Works. Prepared the first draft of both class presentations. I have also worked a lot with grammar and formalities in the various sub-reports, especially in LaTeX. 

\subsection{General statement} 
Everyone worked on everything. Everyone. Best team ever! 